### 2013-09-19 manuscripts/reply/reply.tex
Fleshing out more text for reply.

@@

\subsection*{Final thought on EB}
Given all of this, it is quite clear why one should use caution before
overly criticizing ones choice of priors after having seen the posterior.
This really is a strawman argument.
They were not there before the data were seen.

@@

\section*{Our power analysis}

@@

@@

>>>>

\section*{Hickerson et al.'s re-analysis of the Philippines data}

@@

\subsection*{Final thought on EB}
Given all of the theoretical and practical issues with empirical Bayes
approaches to Bayesian model choice discussed in the proceeding sections, it is
quite clear why one should use caution before overly criticizing an
investigators choice of priors after having seen the posterior.
In a strictly Bayesian world, this is cheating.
As discussed by \citet{Oaks2012}, prior to analysing the data, there was a large
amount of uncertainty regarding the divergence times of the 22 population pairs
under study.
Two the these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
Siler2011,Siler2012,RafeStuart2012}.
\highLight{Any new stuff to add to this list of citations?}.
\citet{Oaks2012} also discuss how the sole use of uniform priors in \msb makes
it very difficult for investigators to express their prior uncertainty without
putting a lot of prior density in regions of improbable parameter space.
The alternative, as shown above, is to risk excluding the truth before even
conducting the analysis.

\section*{Our power analysis}
\citet{Hickerson2013} did present a power analysis in their response, however,
they did not follow the recommendations and conduct a power analysis to
accompany their inference of clustered divergences using the Philippines data
and their empirical Bayesian model-averaging approach.
We present such an analysis here.

Following \citet{Oaks2012}, we simulated 1000 pseudo-replicate datasets with
\divt{} for each of the 22 population pairs randomly drawn from a uniform
distribution, $U(0, \divt{max})$, where \divt{max} was set to: 0.2, 0.4, 0.6,
0.8, 1.0, and 2.0, in \globalcoalunit generations.
All other parameters were identically distributed as the prior.
Following \citet{Hickerson2013} (but avoiding mixing time units), we used five
priors, all of which had priors on population sizes of $\meanDescendantTheta{}
\sim U(0.0001, 0.1)$ and $\ancestralTheta{} \sim U(0.0001, 0.05)$.
Each of these priors had the following priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
For our prior, we simulated $1\e6$ random samples from each of the models
for a total sample of $5\e6$.
For each pseudo-replicate dataset, we retained the 1000 samples from each prior
model with the smallest Euclidean distance from the replicates' summary
statistics, standardizing the statistics using the prior means and standard
deviations of the given model.
Then, for each replicate, we retained the 1000 samples with the smallest
Euclidean distance from the pseudo-observed summary statistics, this time
standardizing the statistics using the prior means and standard deviations
across all five models.
In total, we analyzed 6000 replicate datasets, retaining 1000 model-averaged
posterior samples from each of them.

We find that the approach of \citet{Hickerson2013} to estimate the dispersion
index of divergence times (\vmratio{}) across most of the \divt{max} we
simulated, whether evaluating the unadjusted
(Figure~\ref{figPowerAccOmegaMedian}) or GLM-adjusted
(Figure~\ref{figPowerAccOmegaModeGLM}) posterior estimates.
The method only estimates \vmratio{} relatively well when the simulated
distribution of divergence times is identical to one of the prior models
(Figures~\ref{figPowerAccOmegaMedian}E \& \ref{figPowerAccOmegaModeGLM}E).
This is consistent with the conclusion of \citet{Oaks2012} that \msb lacks
robustness and is highly sensitive to the prior distribution deviating from the
true, underlying distribution of the data.

Furthermore, our results demonstrate that the approach of \citet{Hickerson2013}
consistently infers highly clustered divergences across all the \divt{max} we
simulated (Figure~\ref{figPowerNumExcluded}).
The method is most likely to infer the extreme case of a single divergence event
when populations diverge randomly over the past \globalcoalunit generations.
Even when divergences are random over the past $8\globalpopsize$ generations,
the most likely inference is only two divergence events, and a single 
divergence is still estimated in more than 10\% of the replicates.
It is very interesting to note that as \divt{max} increases, but before the
mode inference is finally pulled away from $\numt{} = 1$, the distribution of
\numt{} estimates closely mirrors the odd U-shaped prior on divergence models
used by \msb (see Figure~\ref{figPowerNumExcluded}E and Oaks et al.'s
\citeyear{Oaks2012} Figure 5B).
This supports the conclusions of \citet{Oaks2012} that this U-shaped
prior coupled with the poor marginal likelihoods of models with many
\divt{} parameters, is a major cause of the method's bias toward
clustered divergence models.

Looking at our simulation results in terms of the posterior probability of the
divergence-time dispersion index supporting the extreme case of one divergence
event (i.e., $p(\vmratio{} < 0.01 \given \ssSpace)$), we find the method
strongly supports one divergence in greater than 27\%
of the replicates across all the \divt{max} we simulated
(Figure~\ref{figPowerOmegaProb}).
Following \citet{Hickerson2013}, We use a Bayes factor of greater than 10 as
the criterion for incorrect inference of a single divergence event.
There is strong support for a single divergence event in more than 90\% of the
replicates when divergences are random over the past $2.4\globalpopsize$
generations, and more than 60\% when over the past $3.2\globalpopsize$
generations or less (Figure~\ref{figPowerOmegaProb}).

Contrary to Hickerson et al.'s \citeyear{Hickerson2013} claim that their
model-averaging approach ``can discriminate complex multispecies histories and
correctly reject synchronous divergence, even when discrete divergence times
differ by much less than \ldots millions of generations,'' our results show
that method is biased toward strongly supporting the extreme case of a single
divergence event when populations diverged random over the last
$8\globalpopsize$ generations.
To roughly put that on the scale for a vertebrate mitochondrial locus, assuming
a mutation rate of $2\e{-8}$ per site per generation, this translates to 5
million generations.
Assuming a mutation rate consistent with nuclear loci of $1\e{-9}$, this is 100
million generations.

The results of our power analysis further demonstrate the
propensity of Hickerson et al.'s \citeyear{Hickerson2013} approach
to exclude true parameter values.
Across all but one of the \divt{max} we simulated, the method excludes the
truth in large proportion of replicates, and across many of the \divt{max} it
will exclude a large proportion of the true divergence time values
(Figure~\ref{figPowerNumExcluded}.
The posterior probability of excluding at least on true divergence value is
also quite high across many of the \divt{max}
(Figure~\ref{figPowerProbExclusion}).
Only when the data are identically distributed as one the prior models does
the method avoid excluding the truth more than 5\% of the time
(Figure~\ref{figPowerNumExcluded}E).

Given our results, we conclude that not only does is the approach of
\citet{Hickerson2013} dangerous in terms of excluding regions of parameter
space containing the true, but still lacks power to detect random variation in
divergence times over the scale of $8\globalpopsize$ generations or more.
This translates to millions of generations for mitochondrial loci, and hundreds
of millions of generations for nuclear loci.

@@

\citet{Hickerson2013} translate their results from units of
\globalcoalunit generations to generations assuming a mutation rate of
$1.92\e{-8}$ mutations per site per generation.
If we tranlate there results to a scale more consistant with rates of mutation
of nuclear loci ($1\e{-9}$), even under the very optimistic prior settings used
by \citet{Hickerson2013} the method can only reliably reject the extreme case
of one divergence event when divergences are random over a period of more than
3 million generations.
Again, considering \citet{Hickerson2013} are assuming prior knowledge that
all population pairs diverged within the past coalescent unit, this
does not seem particularly powerful.

\section*{Lindley's paradox versus sampling error}

\subsection*{The probabilistic argument for sampling error}

@@

\section*{Other clarifications}
\begin{itemize}
    \item saturation plot
    \item different vocabulary (``simultaneous'', etc)
    \item we did not conclude any inference of $\numt{} > 1$ is robust
\end{itemize}

@@

\mFigure{../../response-redux/hickerson-et-al-posterior/mean_by_dispersion.pdf}{
    Hickerson et al.'s \citeyear{Hickerson2013} joint posterior.
}{figJointPosteriorHickerson}
